Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-26 VegOzone.tex
Fix acronym

To measure the risk of damage inflicted to vegetation through ozone, different metrics have been defined. Two main types can be differentiated, concentration-based and exposure-based metrics, e.g., Accumulated Over a Threshold $\mathrm{x}$ ($\mathrm{AOT_x}$) and Phyto-toxic Ozone Dose over a threshold $\mathrm{y}$ ($\mathrm{POD_y}$). Due to their simplicity, concentration-based metrics are still widely used, despite comparisons between the two methods (e.g. $\mathrm{AOT_{40}}$ with $\mathrm{POD_3}$) show that exposure-based metrics are better suited to represent the actual risk to vegetation from ozone, especially in the more climatically extreme parts of Europe \citep{GCB:Mills2010,ICP:MappingManual2017,iFJuran2018}. Most of these previous studies focused on the Mediterranean region.

>>>>

To measure the risk of damage inflicted to vegetation through ozone, different metrics have been defined. Two main types can be differentiated, concentration-based and exposure-based metrics, e.g., Accumulated Ozone Exposure over a threshold of $\mathrm{x}$ ($\mathrm{AOT_x}$) and Phyto-toxic Ozone Dose over a threshold $\mathrm{y}$ ($\mathrm{POD_y}$). Due to their simplicity, concentration-based metrics are still widely used, despite comparisons between the two methods (e.g. $\mathrm{AOT_{40}}$ with $\mathrm{POD_3}$) show that exposure-based metrics are better suited to represent the actual risk to vegetation from ozone, especially in the more climatically extreme parts of Europe \citep{GCB:Mills2010,ICP:MappingManual2017,iFJuran2018}. Most of these previous studies focused on the Mediterranean region.
